Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
update html again

# Results {.tabset .tabset-fade}
```{r, include = FALSE}
# import functions
source("functions.R")

@@

## Descriptive statistics for Empathic Accuracy
```{r, include = FALSE}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

@@

## Variance decomposition in interpersonal accuracy for thoughts, affect, and personality traits

```{r}
# personality
samdata <- rio::import(here::here("data", "samdata.csv"))

@@

sjPlot::tab_model(samEAC_null)

```{r}
# thought

## Interpersonal accuracy for thoughts, affect, and personality traits

@@

## Density plots for random effects will be here

## fit a model for each perceiver
# models_dyad <- 
# samdata %>% 
#   group_by(PerUn) %>% 
#   nest() %>% 
#   mutate(models = map(data, ~ {
#     
#     lm(ptrait ~ targSRrC + AvgtraitC, 
#               data = .x)
#     
#   }
#                       )
#          )
```

@@

summary(samEAC)

@@

```{r}
# thought

@@

>>>>

# Results {.tabset .tabset-fade}

**THIS IS A VERY ROUGH DRAFT :) **

```{r, include = FALSE}
# import functions
source("functions.R")

@@

## Descriptive statistics
```{r, include = FALSE}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

@@

## Variance decomposition

```{r}
# personality
samdata <- import(here::here("data", "samdata.csv"))

@@

sjPlot::tab_model(samEAC_null)
```

```{r}
# thought
eaSRMdata <- import(here::here("data", "d_thought.csv"))

# overall EA
SRMdat1 <- lmer(EA100 ~ 
                   (1|PerUn) + 
                   (1|TarUn) + 
                   (1|DyUn) + 
                   (1|Group), 
                 data = eaSRMdata)

sjPlot::tab_model(SRMdat1)
```

## Interpersonal accuracy

@@

## Density plots for random effects will be placed here

## fit a model for each perceiver
models_dyad <-
samdata %>%
  group_by(PerUn) %>%
  nest() %>%
  mutate(models = map(data, ~ {

    lm(ptrait ~ targSRrC + AvgtraitC,
              data = .x)

  }
                      )
         )
```

@@

sjPlot::tab_model(samEAC)

@@

```{r}
# thought
# baseline accuracy
normEASRM<- lmer(BaselineEA100 ~ 
                   (1|PerUn) + 
                   (1|TarUn) + 
                   (1|DyUn) + 
                   (1|Group), 
                 data = eaSRMdata)

# corrected for baseline
diffEASRM<- lmer(CrrctdEAnoneg ~ 
                    (1|PerUn) + 
                    (1|TarUn) + 
                    (1|DyUn) + 
                    (1|Group), 
                  data = eaSRMdata)

sjPlot::tab_model(normEASRM, diffEASRM)
```

@@

WILL WORK ON THIS LATER.
